1-generate-toys

### 2018-01-23 analysis/analyses/3-score_rules/1-generate-toys.Rmd
small update to score rules

```{r}
toys_blueprint <- tribble(
  ~trajectory_type, ~perturbator_id,
  "simple_linear", "gs",
  "simple_linear", "switch_two_cells",
  "simple_linear", "switch_all_cells",
  "simple_linear", "join_linear",
  "simple_linear", "split_linear",
  "simple_linear", "warp",
  "simple_linear", "hairy",
  "simple_linear", "hairy_small",
  "simple_linear", "hairy_large",
  "simple_linear", "remove_cells",
  "simple_linear", "add_distant_edge",
  "simple_linear", "structure_and_position",
  "bifurcating", "gs",
  "bifurcating", "change_lengths",
  "bifurcating", "change_terminal_lengths",
  "bifurcating", "switch_two_cells",
  "bifurcating", "switch_all_cells",
  "bifurcating", "warp",
  "bifurcating", "hairy",
  "bifurcating", "remove_cells",
  "bifurcating", "add_distant_edge",
  "bifurcating", "structure_and_position",
  "cycle", "gs",
  "cycle", "switch_all_cells",
  "cycle", "break_cycles",
  "cycle", "warp",
  "cycle", "hairy",
  "cycle", "remove_cells",
  "cycle", "add_distant_edge"
) %>% 
  bind_rows(tibble(trajectory_type="simple_linear", perturbator_id=paste0("switch_", percs * 100))) %>%
  bind_rows(crossing(trajectory_type=trajectory_types, perturbator_id=paste0("change_network_", trajectory_types)) %>% mutate(ncells = 5)) %>% 
  rowwise() %>% 
  mutate(
  perturbator=list(get(paste0("perturb_", perturbator_id)))
)

# replicate
nreplicates <- 1
toys <- toys_blueprint %>% slice(rep(1:n(), each=nreplicates)) %>% mutate(
  replicate=seq_len(nrow(.))%%nreplicates,
  toy_category=paste0(trajectory_type, "-", perturbator_id),
  toy_id=paste0(toy_category, "-", replicate)
) %>%
  mutate(ncells=sample(50:500, n(), replace=TRUE))

# generate gold standards and toys, can take some time (for computing the geodesic distances I presume)
# I choose to not do this using mutate because it is much easier to debug using loops
toys$gs <- toys %>% split(seq_len(nrow(toys))) %>% parallel::mclapply(function(row) {
  generate_dataset(row$trajectory_type, row$ncells)
}, mc.cores=8)
#toys$gs <- map2(toys$generator, toys$ncells, ~.x(.y))

>>>>

```{r}
toys_blueprint <- tribble(
  ~trajectory_model, ~perturbator_id,
  "simple_linear", "gs",
  "simple_linear", "switch_two_cells",
  "simple_linear", "switch_all_cells",
  "simple_linear", "join_linear",
  "simple_linear", "split_linear",
  "simple_linear", "warp",
  "simple_linear", "hairy",
  "simple_linear", "hairy_small",
  "simple_linear", "hairy_large",
  "simple_linear", "remove_cells",
  "simple_linear", "add_distant_edge",
  "simple_linear", "structure_and_position",
  "bifurcating", "gs",
  "bifurcating", "change_lengths",
  "bifurcating", "change_terminal_lengths",
  "bifurcating", "switch_two_cells",
  "bifurcating", "switch_all_cells",
  "bifurcating", "warp",
  "bifurcating", "hairy",
  "bifurcating", "remove_cells",
  "bifurcating", "add_distant_edge",
  "bifurcating", "structure_and_position",
  "cycle", "gs",
  "cycle", "switch_all_cells",
  "cycle", "break_cycles",
  "cycle", "warp",
  "cycle", "hairy",
  "cycle", "remove_cells",
  "cycle", "add_distant_edge"
) %>% 
  bind_rows(tibble(trajectory_model="simple_linear", perturbator_id=paste0("switch_", percs * 100))) %>%
  bind_rows(crossing(trajectory_model=trajectory_models, perturbator_id=paste0("change_network_", trajectory_models)) %>% mutate(ncells = 5)) %>% 
  rowwise() %>% 
  mutate(
  perturbator=list(get(paste0("perturb_", perturbator_id)))
)

# replicate
nreplicates <- 1
toys <- toys_blueprint %>% slice(rep(1:n(), each=nreplicates)) %>% mutate(
  replicate=seq_len(nrow(.))%%nreplicates,
  toy_category=paste0(trajectory_model, "-", perturbator_id),
  toy_id=paste0(toy_category, "-", replicate)
) %>%
  mutate(ncells=sample(50:500, n(), replace=TRUE))

# generate gold standards and toys, can take some time (for computing the geodesic distances I presume)
# I choose to not do this using mutate because it is much easier to debug using loops
toys$gs <- toys %>% split(seq_len(nrow(toys))) %>% parallel::mclapply(function(row) {
  dyntoy:::generate_dataset("why", row$trajectory_model, row$ncells)
}, mc.cores=8)
#toys$gs <- map2(toys$generator, toys$ncells, ~.x(.y))
